---
title: "Team A MSMA Greek Yogurt Case"
author: "Jiakang Chen, Chengyu Jiang, Jade Sinskul, Yun Xiao"
date: "11/9/2020"
output: html_document
---

### Read the data
```{r}
library(foreign)
library(haven)
library(devtools)
library(usethis)
library(devtools)
library(ggplot2)
library(ggbiplot)
library(dplyr)
library(psych)
library(stargazer)
df <- read_sav("Desktop/Wegmans Survey (1).sav")
```

### Principle Component Analysis of Question 6 vs Cook
#### Ratings of importance of the attributes when purchasing Greek Yogurt


```{r}
Q6 <- df[47:59] #subset the questions 6
#View(Q6)
Q6names <- names(Q6) #extract column names of question 6
complete.obs <- apply(!is.na(df[,Q6names]),1,all) #find rows with missing values in question 6
table(complete.obs) 
dfnew <- df[complete.obs==TRUE,] #dfnew is a dataframe that contains all the rows that have no missing values in questions 6
```

After removing the missing values, 135 rows are removed. Now there are 940 rows. But we are uncertain of whether the 'dfnew' (sample) are representative of the whole data (population). So we did three Chi-square tests and a correlation difference calculation to test whether the sample is representative.

We did Chi-square tests to compare based on gender, cook/snack, and age.

```{r}
#Gender
popGender<-c(0.1,0.89,0.01)
table(dfnew$Question33Areyou)
sapGender<-c(94/939,836/939,9/939)
chisq.test(sapGender,p=popGender) 

#Cook
popCook <- c(0.49,0.51)
table(dfnew$Question12DoyouuseGreekYogurtforcooking)
sampCook <- c(452/939,487/939)
chisq.test(sampCook,p=popCook)

#Age
popAge <- c(0.015,0.132,0.227,0.276,0.247,0.088,0.015)
table(dfnew$Question32Forclassificationpurposesonlypleaseindicatewhichagegro)
sampAge <- c(15/939,125/939,215/939,262/939,229/939,79/939,15/939)
chisq.test(sampAge,p=popAge)
```

All the three p-values are close to 1, so we can conclude that the sample is not different from the population.

```{r}
#Correlation differences
cor1 <- cor(df[,Q6names],use='complete.obs')
#stargazer(cor1,type='text')
Q6Complete <- df[complete.obs,Q6names]
cor2 <- cor(Q6Complete)
sum(cor1==cor2)/length(cor1)
cor3 <- cor(df[,Q6names],use='pairwise.complete.obs')
sum(abs(cor2-cor3)<0.05)/length(cor1)
sum(abs(cor2-cor3)<0.1)/length(cor1)
```

Cor 1 and cor 2 give the same answer. Cor3 has slightly different numbers. But the missing data does not affect the overall relationships.

```{r}
df1 <- dfnew #assign dfnew to a new dataframe called df1
df1$Cook <- ifelse(dfnew$Question12DoyouuseGreekYogurtforcooking=='Yes',1,0) #assign 1 to Cook and 0 to snack
complete.obsCook <- complete.obs&!is.na(df1$Cook)
complete.obsAll <- complete.obsCook
resultPCA <- prcomp(~.,data=df[complete.obsAll,Q6names],scale.=TRUE,na.action=na.omit)
ggscreeplot(resultPCA) #Elboe rule, we select '6'
```
```{r}
stargazer(resultPCA$rotation[,1:6],type='text')#select 6 PCs
ggbiplot(resultPCA,alpha=.1,ellipse = TRUE)
df1 <- dfnew#assign dfnew to a new dataframe called df1
df1$Cook <- ifelse(dfnew$Question12DoyouuseGreekYogurtforcooking=='Yes',1,0)#assign 1 to Cook and 0 to snack

#Plot PCs with cook/snack
gg1<-ggbiplot(resultPCA,alpha=.4,group=df1$Cook,choices = c(1,2),ellipse = T,ellipse.prob = .1)
#View(df1)
gg1

gg2<-ggbiplot(resultPCA,alpha=.4,group=df1$Cook,choices = c(1,3),ellipse = T,ellipse.prob = .1)
gg2

gg3<-ggbiplot(resultPCA,alpha=.4,group=df1$Cook,choices = c(1,4),ellipse = T,ellipse.prob = .1)
gg3

gg4<-ggbiplot(resultPCA,alpha=.4,group=df1$Cook,choices = c(1,5),ellipse = T,ellipse.prob = .1)
gg4

gg5<-ggbiplot(resultPCA,alpha=.4,group=df1$Cook,choices = c(1,6),ellipse = T,ellipse.prob = .1)
gg5

```

### Perceptional Map of Chobani, Oikos, Foge

```{r}
fage <- df[102:110] #subset rating questions of fage
chobani <- df[114:122] #subset rating questions of chobani
oikos <- df[126:135] #subset rating questions of fage #chobani

colnames(chobani)<-c('Allnatural','Calorielevel','Consistency','Fatlevel','Fruitonthebottom','Price','Proteinlevel','Taste','Texture')
colnames(oikos)<-c('Allnatural','Calorielevel','Consistency','Fatlevel','Fruitonthebottom','Organic','Price','Proteinlevel','Taste','Texture')
colnames(fage)<-c('Allnatural','Calorielevel','Consistency','Fatlevel','Price','Proteinlevel','Sidebysidecup','Taste','Texture') 
fage$brand <- 'fage'
chobani$brand <- 'chobani'
oikos$brand <- 'oikos'
df2<-merge(x=fage,y=chobani,all=T) #df2 contains all fage and chobani ratings and the brand names
#View(df2)
df3<-merge(x=df2,y=oikos,all=T) #df3 contains all the three brand names and ratings
#View(df3)

rating.sc<-df3
rating.sc[,-9]<-scale(df3[,-9]) #only take the ratings
brand.mean <- aggregate(rating.sc[,-9],list(rating.sc[,9]),mean,na.rm=T) #calculate the mean of ratings of each attribute of each brand
brand.mean

rownames(brand.mean)<-c('chobani','fage','oikos') #change rownames to brand names
brand.mean<-brand.mean[,-1] #remove uneccessary data
brand.mean<-brand.mean[,1:8] #only keep the columns with no zeros
rating.pc<-prcomp(brand.mean,scale=T) #conduct the perceptional map
summary(rating.pc) #We can see PC1 and PC2 tell most the the variances 
plot(rating.pc,type='l') #elbow rule, we take 2 PCs
biplot(rating.pc,cex=c(1,0.9)) #draw the map
abline(h=0)
abline(v=0)

```

